Browsernative Microservices

### 2017-02-13 build/paper.tex
pdf/tex build

Data Management in Microservice follows the same modular philosophy like
the conceptual implementation. As mentioned earlier different bounded
contexts make different assumptions of the underlying model. A
\emph{browsernative microservices} takes this thought even further and
expands it to the variety of devices. Decentralized decisions about
conceptual models demand for decentralized data storage
decisions.{[}4{]} Since network roundtrips are costly it is a good
advice to only query as much data as needed and cache as much as
possible.

``Microservices prefer letting each service manage its own
database.''{[}Fowler2014{]} Ben Issa, chief architect of ING Australia
emphasizes this pragmatism on APIs in a conference talk. At ING the
frontend demands drive the APIs, APIs are produces automatically and not
even Issa knows how many APIs exists.{[}9{]} They are using a pattern
called \textbf{backend for frontends} allowing the team working on a
given UI also handle the server-side components.{[}3, p. 72{]} The
perception on backend might change therefore from embodying logic to a
data-silo only.

@@

The upcoming microservice example assumes a generic build-in API next to
the build-in frontend components. Instead of gluing frontend and backend
together on runtime, the microservice is designed holistically
containing both ends. To reduce network calls especially for mobile
devices it is a good advice to cache data via a global Service Worker.
Revamping offline capabilities even further data can be stored in a
browser based database like PouchDB. For the sake of simplicity data
management won't be conducted into depth throughout this paper.

@@

Working in a JS heavy infrastructure demands for optimazation to avoid
unexpected side-effects like the \emph{flash of unstyled content
(FOUC)}. Googles Polymer propagates the a general-purpose \textbf{PRLP
pattern}\footnote{\href{https://www.polymer-project.org/1.0/toolbox/server}{PRLP
  pattern}}:

@@

Using modular web architecture isn't a perceptually new approach.

Angular, React

Interopt

Freedom of choice

@@

\KeywordTok{<script>}
 \CommentTok{// Switched to anonymous class notation}
 \CommentTok{// for keeping associated code together.}
 \VariableTok{customElements}\NormalTok{.}\AttributeTok{define}\NormalTok{(}\StringTok{'hello-world'}\OperatorTok{,}
  \KeywordTok{class} \KeywordTok{extends} \NormalTok{HTMLElement }\OperatorTok{\{}
   \AttributeTok{constructor}\NormalTok{() }\OperatorTok{\{}
      \KeywordTok{super}\NormalTok{()}\OperatorTok{;}
    \KeywordTok{this}\NormalTok{.}\AttributeTok{attachShadow}\NormalTok{(}\OperatorTok{\{}\DataTypeTok{mode}\OperatorTok{:} \StringTok{'open'}\OperatorTok{\}}\NormalTok{)}\OperatorTok{;}
    \KeywordTok{const} \NormalTok{template }\OperatorTok{=}
     \VariableTok{document}\NormalTok{.}\AttributeTok{querySelector}\NormalTok{(}\StringTok{'#hello'}\NormalTok{)}\OperatorTok{;}
    \KeywordTok{this}\NormalTok{.}\AttributeTok{shadowRoot}
     \NormalTok{.}\AttributeTok{appendChild}\NormalTok{(}\VariableTok{template}\NormalTok{.}\AttributeTok{content}\NormalTok{)}\OperatorTok{;}
   \OperatorTok{\}}
  \OperatorTok{\}}\NormalTok{)}\OperatorTok{;}
\OperatorTok{<}\SpecialStringTok{/script>}
\end{Highlighting}
\end{Shaded}

@@

After grasping the principles and some technical background the paper
should illustrate a practical example to \emph{browsernative
microservices}. Googles library Polymer is a good start to learn about
web components. They even offer a command line tool for creating a
polymer skeleton. One of their most famous proof of concept is the
so-called \href{https://shop.polymer-project.org/}{Polymer Shop} which
is a fully-fledged online shop nested within a single custom element
\texttt{\textless{}shop-app\textgreater{}}. It has some elements for
routing, managing view, service worker caching, theming, etc. The whole
shop runs as a single application only fetching and sending resources
but never reloading altogether. Let's assume we work in a sales
engineering team of the Polymer Shop and need to rebuild checkout
process.

@@

Translated into a raw custom element HTML structure, the microservice
might light like:

@@

Pretty straight forward.

http://www.pocketjavascript.com/blog/2015/11/23/introducing-pokedex-org

bare minimum of centralized management of these services

>>>>

Data Management in Microservice follows the same modular philosophy like
the conceptual implementation. As mentioned earlier different bounded
contexts make different assumptions of the underlying model. A
\emph{browsernative microservices} takes this idea even further and
expands it to the fragmented world of electronic devices. Decentralized
decisions about conceptual models demand for decentralized data storage
decisions.{[}4{]} Todays web architectures aims to leverage an
increasing amout of processing to the client to avoid time-consuming
roundtrips especially in mobiles networks.\footnote{Latency numbers:
  https://gist.github.com/jboner/2841832} Since network roundtrips are
costly it is a good advice to only query as much data as needed and
cache as much as possible.

``Microservices prefer letting each service manage its own
database.''{[}Fowler2014{]} Ben Issa, chief architect of ING Australia
emphasizes this pragmatism on APIs in a conference talk. At ING the
frontend demands drive the backend APIs, APIs are produces automatically
and not even Issa knows how many APIs exists.{[}9{]} They are using a
pattern called \textbf{backend for frontends} allowing the team working
on a given UI also handle the server-side components.{[}3, p. 72{]} The
perception on backend might change therefore from embodying logic to a
data-silo only.

@@

The simplified microservice example later in this paper assumes a
generic build-in API next to the build-in frontend components. Instead
of gluing frontend and backend together on runtime, the microservice is
designed holistically containing both front- and backends. To reduce
network calls especially for mobile devices it is a good advice to cache
data via a global Service Worker. Revamping offline capabilities even
further data can be stored in a browser based database like PouchDB. For
the sake of simplicity data management won't be explored into depth
throughout this paper.

@@

Working in a JS heavy infrastructure demands for optimization to avoid
unexpected side-effects like the \emph{flash of unstyled content
(FOUC)}. Googles Polymer propagates the a general-purpose \textbf{PRLP
pattern}\footnote{\href{https://www.polymer-project.org/1.0/toolbox/server}{PRLP
  pattern}}:

@@

Microservices tend to become smaller over time. An evolutionary design
approach puts emphasizes on decomposition and scrapping the service.
``The key property of a component is the notion of independent
replacement and upgradeability.''{[}4{]} Therefore we can safely change
and chop services. Lazy parts of the system which won't change to often
should be separated from parts undergoing a lot of churn.{[}4{]} Parts
that needs coupled changes could should be moved together or should be
even merged.

This flexible approach fits good in the world of browser based
development. In the last decade we have seen a lot of of changes in the
way we develop for the web. New technologies like Angular and React are
handy to use but add some future uncertainty.

In the next section of this paper a lot of standardized technologies
around the concept of \textbf{Web Components} for the browsers will be
described. \emph{Browsernative Microservices} should be perceived as
complementary technology. Contrary to Angular, React and other
frameworks they have a strong interop with existing systems and can be
used with them together.

Andrew Rota, developer at Wayfair, came up with the idea to compose
small web components around a managing React system.{[}11{]} As web
components are native elements there is no difference to use a native
\texttt{button} or a native \texttt{custom-button}. With this pattern a
web developer can make use of the encapsulated advantages of web
components while still making use of the declarative event management
from various frameworks. Whatever new framework will be on the rise
within the next years, this approach allows rapid decomposition and
reassembling.

@@

\KeywordTok{<script>}
 \CommentTok{// Switched to anonymous class notation}
 \CommentTok{// for keeping associated code together.}
 \VariableTok{customElements}\NormalTok{.}\AttributeTok{define}\NormalTok{(}\StringTok{'hello-world'}\OperatorTok{,}
  \KeywordTok{class} \KeywordTok{extends} \NormalTok{HTMLElement }\OperatorTok{\{}
   \AttributeTok{constructor}\NormalTok{() }\OperatorTok{\{}
    \KeywordTok{super}\NormalTok{()}\OperatorTok{;}
    \KeywordTok{this}\NormalTok{.}\AttributeTok{attachShadow}\NormalTok{(}\OperatorTok{\{}\DataTypeTok{mode}\OperatorTok{:} \StringTok{'open'}\OperatorTok{\}}\NormalTok{)}\OperatorTok{;}
    \KeywordTok{const} \NormalTok{helloTemplate }\OperatorTok{=}
     \VariableTok{document}\NormalTok{.}\AttributeTok{querySelector}\NormalTok{(}\StringTok{'#hello'}\NormalTok{)}\OperatorTok{;}
    \KeywordTok{this}\NormalTok{.}\AttributeTok{shadowRoot}
     \NormalTok{.}\AttributeTok{appendChild}\NormalTok{(}\VariableTok{helloTemplate}\NormalTok{.}\AttributeTok{content}\NormalTok{)}\OperatorTok{;}
   \OperatorTok{\}}
  \OperatorTok{\}}\NormalTok{)}\OperatorTok{;}
\OperatorTok{<}\SpecialStringTok{/script>}
\end{Highlighting}
\end{Shaded}

@@

After getting some confidence in microservice principles and some
technical background the paper should illustrate a practical example to
\emph{browsernative microservices}. Googles library Polymer is a good
place for learning about web components in depth and make use of their
simple command line tools. One of their most famous proof of concept is
the so-called \href{https://shop.polymer-project.org/}{Polymer Shop}
which is a fully-fledged online shop nested within a single custom root
element \texttt{\textless{}shop-app\textgreater{}}. It has some elements
for routing, managing view, service worker caching, theming, etc. The
whole shop runs as a single application only fetching and sending
resources but never reloading altogether. Let's assume we work in a
sales engineering team of the Polymer Shop and need to rebuild the
checkout microservice.

@@

Translated into a raw custom element HTML structure, the top-level
microservice might look like the following snippet:

@@

\subsection{Service Root}\label{service-root}

The core concept of the newly created \texttt{shop-checkout} is a clean
MVC pattern where the model is a worker managed by the root element. The
role of the root element offers a bare minimum of centralized
orchestration as a \textbf{kind of message broker}. Messages from child
nodes will just forwarded to the worker and answers passed back to the
child nodes. Therefore, the basic microservice communication looks like
this

\begin{verbatim}
VIEW root           |               MODEL worker
                    |
Event  --------Event msg--------->    Msg
    |               |               Handler
    |               |                   |
Idle                |               Effekt
    |               |                   |
  Msg               |                   |
Handler <-----Action msg----------  Action                                      
                    |                   
                    |
\end{verbatim}

Effects are yielded by the asynchronous operation of messages and create
actions returned to sender. Effects can be created by external messages,
like subscription to an WebSocket, too. Effects may be created by
fetching additional resources from the server. The VIEW side of the root
element forwards all the messages and won't be bothered about the
content.
